---
editor: visual
---

```{r}
#| label: set-up-results
#| echo: false
library(targets)
library(tarchetypes)
library(gt)

```

## Results

### PART 1: General models

### Functional group richness effect

Test overall effects of number of functional groups (functional group richness) on standing biomass across the climate grid.

```{r}
#| label: fig-fg-fichness-effects
#| fig-cap: "Estimated effects from the mixed-effects model of number of functional groups on standing biomass. The model coefficients with confidence intervals for functional group richness, precipitation, and temperature and their interactions are shown."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
tar_load(fig_fg_richness_effects)

# Display plot
fig_fg_richness_effects
```

```{r}
#| label: fg-richness-tidy-table
#| echo: false
#| warning: false
#| message: false

# Load the tidy model output for fg_richness
if (!exists("fg_richness_tidy")) tar_load(fg_richness_tidy)

pretty_model_table(fg_richness_tidy)

```

### Functional group identity effects

```{r}
#| label: fg-identity-tidy-table
#| echo: false
#| warning: false
#| message: false

# Load the tidy model output for fg_identity
if (!exists("fg_identity_tidy")) tar_load(fg_identity_tidy)

pretty_model_table(fg_identity_tidy)
```

```{r}
#| label: fig-fg-identity-interactions
#| fig-cap: "Interaction effects from the mixed-effects model for functional group identity on standing biomass. The plot displays estimated interaction effects between functional group identity and environmental variables."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
if (!exists("fig_fg_identity_interactions")) tar_load(fig_fg_identity_interactions)

# Display plot
fig_fg_identity_interactions
```

### Functional group biomass

```{r}
#| label: fig-fg-biomass-effects
#| fig-cap: "Estimated effects from the mixed-effects model of functional group biomass on standing biomass. The model coefficients with confidence intervals for functional group biomass, precipitation, and temperature and their interactions are shown."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
if (!exists("fig_fg_biomass_effects")) tar_load(fig_fg_biomass_effects)

# Display plot
fig_fg_biomass_effects
```

```{r}
#| label: fig-fg-biomass-interactions
#| fig-cap: "Interaction effects from the mixed-effects model for functional group biomass on standing biomass. The plot displays estimated interaction effects between functional group biomass and environmental variables."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
if (!exists("fig_fg_biomass_interactions")) tar_load(fig_fg_biomass_interactions)

# Display plot
fig_fg_biomass_interactions
```

```{r}
#| label: fg-biomass-tidy-table
#| echo: false
#| warning: false
#| message: false

# Load the tidy model output for fg_biomass
if (!exists("fg_biomass_tidy")) tar_load(fg_biomass_tidy)

pretty_model_table(fg_biomass_tidy)
```

### Part 2: Single group effects

## Graminoids only

### Functional group richness effect (Graminoids only)

```{r}
#| label: fig-fg-richness-G-effects
#| fig-cap: "Estimated effects from the mixed-effects model of number of functional groups (graminoids only) on standing biomass. The model coefficients with confidence intervals for functional group richness, precipitation, and temperature and their interactions are shown."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
if (!exists("fig_fg_richness_G_effects")) tar_load(fig_fg_richness_G_effects)

# Display plot
fig_fg_richness_G_effects
```

```{r}
#| label: fg-richness-G-tidy-table
#| echo: false
#| warning: false
#| message: false

# Load the tidy model output for fg_richness_G
if (!exists("fg_richness_G_tidy")) tar_load(fg_richness_G_tidy)

pretty_model_table(fg_richness_G_tidy)
```

### Functional group identity effect (Graminoids only)

```{r}
#| label: fig-fg-identity-G-effects
#| fig-cap: "Estimated effects from the mixed-effects model of functional group identity (graminoids only) on standing biomass. The model coefficients with confidence intervals for functional group identity, precipitation, and temperature and their interactions are shown."
#| echo: false
#| warning: false
#| message: false

# Load the figure from targets
if (!exists("fig_fg_identity_G_effects")) tar_load(fig_fg_identity_G_effects)

# Display plot
fig_fg_identity_G_effects
```

```{r}
#| label: fg-identity-G-tidy-table
#| echo: false
#| warning: false
#| message: false

# Load the tidy model output for fg_identity_G
if (!exists("fg_identity_G_tidy")) tar_load(fg_identity_G_tidy)

pretty_model_table(fg_identity_G_tidy)
```
